Random Generation of Rich \\ Abstract Data Type Values

### 2019-02-01 paper/casestudies.tex
Minor fixes

We evaluate how including additional structural information when generating a
set of random test cases (often referred as a \emph{corpus}) affects the code
coverage obtained when testing a given target program.
%
For that, we considered two external programs which expect highly structured
inputs, namely \emph{GNU CLISP}---the GNU Common Lisp
compiler\footnote{\href{https://www.gnu.org/software/gcl/}{https://www.gnu.org/software/gcl/}},
and \emph{HTML Tidy}
\footnote{\href{http://www.html-tidy.org}{http://www.html-tidy.org}}---a well
known HTML refactoring and correction utility.
%
We remark that these applications are not written in Haskell.
%
However, there exist Haskell libraries defining ADTs encoding their input
structure, i.e., Lisp and HTML values respectively. These libraries are:
\emph{hs-zuramaru}\footnote{\href{http://hackage.haskell.org/package/zuramaru}{http://hackage.haskell.org/package/zuramaru}},
implementing an embedded Lisp interpreter for a small subset of this programming
language, and
\emph{html}\footnote{\href{http://hackage.haskell.org/package/html}{http://hackage.haskell.org/package/html}},
defining a combinator library for constructing HTML values.
%
These libraries also come with serialization functions to map Haskell values
into corresponding test case files.

We firstly compiled instrumented versions of the target programs in a way that
they also return the execution path followed in the source code every time we
run them with a given input test case.
%
This let us distinguish the amount of different execution paths that a randomly
generated corpus can trigger.
%
We then used the ADTs defined on the chosen libraries to derive random
generators using \dragen and \dragenp, including structural information
extracted from the library's codebase in the case of the latter.
%
Then, we proceeded to evaluate the code coverage triggered by independent,
randomly generated corpora of different sizes varying from 100 to 1000 test
cases each.
%
In order to remove any external bias, we derived generators optimized to follow
\emph{a uniform distribution of constructors (and pattern matchings or function
  calls in the case \dragenp), and carefully adjusted their generation sizes to
  match the average test case size in bytes}.
%
This way, any noticeable difference in the code coverage can be attributed to
the present (or lack thereof) structural information when generating the test
cases.
%
Additionally, to achieve statistical significance we repeated each experiment 30
times with independently generated sets of random test cases.

\begin{figure*}[t]
  \vspace{-5pt}%
  \centering
  \input{tikz/lisp.tex}
  \hspace{5pt}%
  \input{tikz/html.tex}
  \caption{Path coverage comparison between \dragen (\ref{exp:dragen}) and
    \dragenp (\ref{exp:dragenp}). }
  \label{fig:coverage}
  \vspace{-10pt}%
\end{figure*}
%
Fig. \ref{fig:coverage} illustrates the mean number of different execution paths
triggered for different combinations of corpus size and derivation tool,
including error bars indicating the standard error of the mean on each case.
%
We proceed to describe each case study and our findings in detail as follows.

@@

Our chosen library encodes Lisp S-expressions essentially as lists of symbols,
represented as plain strings; and literal values like booleans or integers.
%
In order to interpret Lisp programs, this unified representation of data and
code requires this library to pattern match against common patterns like
let-bindings, if-then-else expressions and arithmetic operators among others.
%
In particular, each one of these patterns match a against special symbol of the
Lisp syntax like |"let"|, |"if"| or |"+"|; and their corresponding
sub-expressions.
%
We extracted this structural information and included it into the generation
specification of our random Lisp values---which were generated by randomly
picking from a total of 6 data constructors and 8 different pattern matchings.
%
By doing this, we obtained a code coverage improvement of approximately $4\%$
using \dragenp with respect to the one obtained with \dragen (see Figure
\ref{fig:coverage} (a)).
%
While it seems an small improvement, we argue that an improvement of $4\%$ is
not negligible considering (a) the little effort that took us to specify the pattern
matchings and (b) that we are testing a compiler.
%it is worth noticing that we are generating
%highly structured inputs, i.e., Lisp programs.
%
%When testing interpreters,
%\todo[inline, author=AM]{Shall we say anything justifing this little
%  improvement?}

@@

With these results we are confident that including the structural information
present on the user codebase improves the testing performance.
%
%% Space reasons
%We consider that our approach is particularly useful when the data types
%encoding the shape of our data are vague or not sufficiently structured to be
%used to derive powerful random generators with the common derivation techniques
%based only on ADT definitions.

>>>>

We evaluate how including additional structural information when generating a
set of random test cases (often referred as a \emph{corpus}) affects the code
coverage obtained when testing a given target program.
%
For that, we considered two external programs which expect highly structured
inputs, namely \emph{GNU
  CLISP} \footnote{\href{https://www.gnu.org/software/gcl/}{https://www.gnu.org/software/gcl/}}---the
GNU Common Lisp compiler, and \emph{HTML Tidy}
\footnote{\href{http://www.html-tidy.org}{http://www.html-tidy.org}}---a well
known HTML refactoring and correction utility.
%
We remark that these applications are not written in Haskell.
%
However, there exist Haskell libraries defining ADTs encoding their input
structure, i.e., Lisp and HTML values respectively. These libraries are:
\emph{hs-zuramaru}\footnote{\href{http://hackage.haskell.org/package/zuramaru}{http://hackage.haskell.org/package/zuramaru}},
implementing an embedded Lisp interpreter for a small subset of this programming
language, and
\emph{html}\footnote{\href{http://hackage.haskell.org/package/html}{http://hackage.haskell.org/package/html}},
defining a combinator library for constructing HTML values.
%
These libraries also come with serialization functions to map Haskell values
into corresponding test case files.

We firstly compiled instrumented versions of the target programs in a way that
they also return the execution path followed in the source code every time we
run them with a given input test case.
%
This let us distinguish the amount of different execution paths that a randomly
generated corpus can trigger.
%
We then used the ADTs defined on the chosen libraries to derive random
generators using \dragen and \dragenp, including structural information
extracted from the library's codebase in the case of the latter.
%
Then, we proceeded to evaluate the code coverage triggered by independent,
randomly generated corpora of different sizes varying from 100 to 1000 test
cases each.
%
In order to remove any external bias, we derived generators optimized to follow
\emph{a uniform distribution of constructors (and pattern matchings or function
  calls in the case \dragenp), and carefully adjusted their generation sizes to
  match the average test case size in bytes}.
%
This way, any noticeable difference in the code coverage can be attributed to
the presence (or lack thereof) structural information when generating the test
cases.
%
Additionally, to achieve statistical significance we repeated each experiment 30
times with independently generated sets of random test cases.

\begin{figure*}[t]
  \vspace{-5pt}%
  \centering
  \input{tikz/lisp.tex}
  \hspace{5pt}%
  \input{tikz/html.tex}
  \caption{Path coverage comparison between \dragen (\ref{exp:dragen}) and
    \dragenp (\ref{exp:dragenp}). }
  \label{fig:coverage}
  \vspace{-10pt}%
\end{figure*}
%
Figure \ref{fig:coverage} illustrates the mean number of different execution
paths triggered for different combinations of corpus size and derivation tool,
including error bars indicating the standard error of the mean on each case.
%
We proceed to describe each case study and our findings in detail as follows.

@@

Our chosen library encodes Lisp S-expressions essentially as lists of symbols,
represented as plain strings; and literal values like booleans or integers.
%
In order to interpret Lisp programs, this unified representation of data and
code requires this library to pattern match against common patterns like
let-bindings, if-then-else expressions and arithmetic operators among others.
%
In particular, each one of these patterns match a against special symbol of the
Lisp syntax like |"let"|, |"if"| or |"+"|; and their corresponding
sub-expressions.
%
We extracted this structural information and included it into the generation
specification of our random Lisp values---which were generated by randomly
picking from a total of 6 data constructors and 8 different pattern matchings.
%
By doing this, we obtained a code coverage improvement of approximately $4\%$
using \dragenp with respect to the one obtained with \dragen (see Figure
\ref{fig:coverage} (a)).
%
While it seems an small improvement, we argue that an improvement of $4\%$ is
not negligible considering (a) the little effort that took us to specify the
pattern matchings and (b) that we are testing a full-fledged compiler.
%it is worth noticing that we are generating
%highly structured inputs, i.e., Lisp programs.
%
%When testing interpreters,
%\todo[inline, author=AM]{Shall we say anything justifing this little
%  improvement?}

@@

With these results we are confident that including the structural information
present on the user codebase improves the overall testing performance.
%
%% Space reasons
%We consider that our approach is particularly useful when the data types
%encoding the shape of our data are vague or not sufficiently structured to be
%used to derive powerful random generators with the common derivation techniques
%based only on ADT definitions.

### 2019-02-01 paper/introduction.tex
Minor fixes

% Scenario of random testing
Random testing is a promising approach for finding bugs
\cite{HughesNSA16,HughesPAN16,ArtsHNS15}.
%
\quickcheck \cite{ClaessenH00} is the dominant tool of this sort used by the
Haskell community.
%
It requires developers to specify (i) \emph{testing properties} describing
programs expected behavior and (ii) \emph{random data generators} based on the
\emph{types} of the expected inputs (e.g., an integer, an string,
etc.). %, e.g., an integer, an string, or an abstract data type (ADT).
%
\quickcheck then generates random test cases and reports violating testing
properties.

>>>>

% Scenario of random testing
Random testing is a promising approach for finding bugs
\cite{HughesNSA16,HughesPAN16,ArtsHNS15}.
%
\quickcheck \cite{ClaessenH00} is the dominant tool of this sort used by the
Haskell community.
%
It requires developers to specify (i) \emph{testing properties} describing
programs' expected behavior and (ii) \emph{random data generators} based on the
\emph{types} of the expected inputs (e.g., an integer, an string,
etc.). %, e.g., an integer, an string, or an abstract data type (ADT).
%
\quickcheck then generates random test cases and reports violating testing
properties.

### 2019-02-01 paper/randomtesting.tex
Minor fixes

\end{code}
%
The type |Html| allows to build pages via four possible constructions:
|Text|---which represents plain text values---, |Single| and |Tag|---which
represent singular and paired HTML tags, respectively---, and |Join|---which
concatenates two HTMLs pages one after another.
%
% In the previous definition, we declare |Html| as the sum of four possible
% constructions: |Text| represents plain text values. |Sing| and |Tag| represent
% singular and paired Html tags, and |Join| concats two expression one after
% another.
% %
% We only encode a very small subset of the actual Html specification for
% illustrative reasons.
% %
In Haskell, |Text|, |Single|, |Tag|, and |Join| are known as \emph{data
  constructors} (or constructors for short) and are used to distinguish which
variant of the ADT we are constructing.
%
Each data constructor is defined as a product of zero or more types known as
\emph{fields}.
%
For instance, |Text| has a field of type |String|, whereas |Join| has two
recursive fields of type |Html|.
%
In general, we will say that a data constructor with no recursive fields is
\emph{terminal}, and \emph{non-terminal} or \emph{recursive} if it has at least
one field of such nature.
%
With this representation, the example page \texttt{<html>hello<hr>bye</html>}
can be encoded as:
%
\begin{code}
Tag "html" (Join (Join
  (Text "hello") (Single "hr")) (Text "bye"))
\end{code}
%
% Additionally, we can define a function |render| to serialize |Html| values as
% follows:
% %
% \begin{code}
% render :: Html -> String
% render (Text t) = t
% render (Sing t) = "<" ++ t ++ ">"
% render (Join x y) = render x ++ render y
% render (Tag t x)
%   = "<" ++ t ++ ">" ++ render x ++ "</" ++ t ++ ">"
% \end{code}

>>>>

\end{code}
%
The type |Html| allows to build pages via four possible constructions:
|Text|---which represents plain text values---, |Single| and |Tag|---which
represent singular and paired HTML tags, respectively---, and |Join|---which
concatenates two HTML pages one after another.
%
% In the previous definition, we declare |Html| as the sum of four possible
% constructions: |Text| represents plain text values. |Sing| and |Tag| represent
% singular and paired Html tags, and |Join| concats two expression one after
% another.
% %
% We only encode a very small subset of the actual Html specification for
% illustrative reasons.
% %
In Haskell, |Text|, |Single|, |Tag|, and |Join| are known as \emph{data
  constructors} (or constructors for short) and are used to distinguish which
variant of the ADT we are constructing.
%
Each data constructor is defined as a product of zero or more types known as
\emph{fields}.
%
For instance, |Text| has a field of type |String|, whereas |Join| has two
recursive fields of type |Html|.
%
In general, we will say that a data constructor with no recursive fields is
\emph{terminal}, and \emph{non-terminal} or \emph{recursive} if it has at least
one field of such nature.
%
With this representation, the example page \texttt{<html>hello<hr>bye</html>}
can be encoded as:
%
\begin{code}
Tag "html" (Join (Join
  (Text "hello") (Single "hr")) (Text "bye"))
\end{code}
%
% Additionally, we can define a function |render| to serialize |Html| values as
% follows:
% %
% \begin{code}
% render :: Html -> String
% render (Text t) = t
% render (Sing t) = "<" ++ t ++ ">"
% render (Join x y) = render x ++ render y
% render (Tag t x)
%   = "<" ++ t ++ ">" ++ render x ++ "</" ++ t ++ ">"
% \end{code}

### 2019-02-01 paper/relatedwork.tex
Minor fixes

%
% GodelTest
%
From the practical point of view, Feldt and Poulding propose \emph{G\"odelTest}
\cite{feldt2013}, a search-based framework for generating biased data.
%
% \emph{G\"odelTest} uses non-determinism to generate a wide range of data structures.
%
Similar to our approach, \emph{G\"odelTest} works by optimizing the parameters
governing the desired biases on the generated data.
%
However, the optimization mechanism uses meta-heuristic search to find the best
parameters at runtime.
%
\dragenp on the other hand implements an analytic and composable prediction
mechanism that is used only used at compile time to optimize the generation
parameters, thus avoiding performing any kind of runtime reinforcement.

%
% DART
%
Directed Automated Random Testing (DART) is a technique that combines random
testing with symbolic execution for C programs \cite{godefroid2005dart}.
%
It requires instrumenting the target programs in order to introduce testing
assertions and obtain feedback from previous testing executions, which is used
to explore new paths in the source code.
%
This technique has been shown to be remarkably useful, Although it forces a
strong coupling between the testing suite and the target code.
%
Our tool intends to provide better random generation of values following an
undirected fashion, without having to instrument the target code, but still
extracting useful structural information from it.

>>>>

%
% GodelTest
%
From the practical point of view, Feldt and Poulding propose \emph{G\"odelTest}
\cite{feldt2013}, a search-based framework for generating biased data.
%
% \emph{G\"odelTest} uses non-determinism to generate a wide range of data structures.
%
Similar to our approach, \emph{G\"odelTest} works by optimizing the parameters
governing the desired biases on the generated data.
%
However, the optimization mechanism uses meta-heuristic search to find the best
parameters at runtime.
%
\dragenp on the other hand implements an analytic and composable prediction
mechanism that is only used at compile time to optimize the generation
parameters, thus avoiding performing any kind of runtime reinforcement.

%
% DART
%
Directed Automated Random Testing (DART) is a technique that combines random
testing with symbolic execution for C programs \cite{godefroid2005dart}.
%
It requires instrumenting the target programs in order to introduce testing
assertions and obtain feedback from previous testing executions, which is used
to explore new paths in the source code.
%
This technique has been shown to be remarkably useful, although it forces a
strong coupling between the testing suite and the target code.
%
Our tool intends to provide better random generation of values following an
undirected fashion, without having to instrument the target code, but still
extracting useful structural information from it.

### 2019-02-01 paper/synthesis.tex
Minor fixes

Vector $E[G_0]$ represents the initial distribution of constructors that our
generator produces, which simply consists of the generation probability of each
one.
%
The interesting aspect of the prediction mechanism is encoded in the matrix $M$,
known as a the \emph{mean matrix} of this stochastic process.
%
$M$ is a squared matrix with as rows and columns as different data constructors
involved in the generation process.
%
Each element $M_{i,j}$ of this matrix encodes the average number of data
constructors of kind $j$ that gets generated in a given generation, provided that we
generated a constructor of kind $i$ at the previous one.
%
In this sense, this matrix encodes the ``branching'' behavior of our random
generation from one generation to the next one.
%
Each element of the matrix can be automatically calculated by exploiting ADT
definitions. % \cite{DBLP:conf/haskell/MistaRH18}
%
% ---specially the recursive fields---
%
as well as the individual probability of generating each constructor.
%
For instance, the average number of |Text| data constructors that we will
generate provided that we generated a |Join| data constructor on the previous
level is calculated as follows:
%
$$ M_{\mathrm{Join, Text}} = 2\cdot p_{\mathrm{Text}} $$
%
where $2$ is the number of holes present when generating a partial ADT value
|Join| (i.e., |Join hole hole|) and $p_{\mathrm{Text}}$ is the probability of
individually generating the constructor |Text|.
%
This pattern can be used to build the rest of the mean matrix as well.

@@

each different pattern matching and function call as shown in Fig.

@@

The new cells are filled as before: we need to consider the amount of holes when
generating partial pattern matching and function calls as well as their
individual probabilities.
%
% Fortunately, it is possible to follow the same pattern as we did on our original
% work, this time considering the amount of recursive pattern variables if it the
% case of a pattern matching value being a father individual, and the amount of
% recursive arguments if we deal with a abstract interface function call as a
% father individual.
%
For instance, if we consider $P_j$ as the second pattern of function |simplify|
and $F_1$ as function |div|, then the marked cell above has the value
$2\cdot p_{div}$, i.e., the amount of holes in the partially generated pattern
|(Join (Join (Text s) hole) hole)|, where |s| is some random string, times the
probability to generate a call to function |div|.
%
The rest of this matrix can be computed analogously.

@@

As another contribution, we found that the whole prediction process can be
factored in terms of two vectors $\beta$ and $\mathcal{P}$, such that $\beta$
represents the number of holes in each partial ADT value that we generate,
whereas $\mathcal{P}$ simply represents the probability of generating that
partial ADT value.% (this probability can be easily calculated based on the
% generation frequencies used in the random generator).
%
Then, the equation \ref{eqn:prediction} can be rewritten as:
%
\begin{align*}
  E[G_n]^T = \beta^T \cdot (\beta \cdot \mathcal{P}^T)^{n}
\end{align*}
%
% The vector $\beta$ can be obtained by analyzing the shape (namely holes) of each
% source of structural information that we consider, and joining them together.
%
For instance, $\beta$ and $\mathcal{P}$ for our generation specification of HTML
values are as shown in Fig. \ref{fig:vectors}.
%
We note |simplify1| and |simplify2| to the patterns occurring in the first and
second clauses of |simplify|, respectively.
%(Dashed lines indicate the composition of the diffent sub-vectors
%that are calculated separately).

@@

It is possible to provide an overall prediction of the expected number of
constructors when restricting the generation process to only bare data
constructors and pattern matching values.
%
To achieve that, we should stop considering pattern matching values as atomic
constructions and start seeing them as compositions of several data
constructors.
%
In that manner, it is possible to obtain the expected \emph{total} number of
generated data constructors that our generators will produce---regardless if they
are generated on their own, or as part of a pattern matching value.
%
We note this number as $E^\downarrow\![\_]$ and, to calculate it, we only need
to add the expected number of bare constructors that are included within each
pattern matching.
%
For instance, we can calculate the total expected number of constructors |Text|
and |Join| that we will generate by simply expanding the expected number of
generated pattern matching values $simplify\#1$ and $simplify\#2$ into their
corresponding data constructors:
%
{\small
  \begin{alignat*}{4}
    &E^\downarrow\!\left[ |Text| \right]
    &= E\left[ |Text| \right]
      &+ 2 \cdot E\!\left[ |simplify1| \right]\
      &+\ 1 \cdot E\!\left[ |simplify2| \right] \\
    &E^\downarrow\!\left[ |Join| \right]
    &= E\left[ |Join| \right]
      &+ 1 \cdot E\!\left[ |simplify1| \right]\
      &+\ 2 \cdot E\!\left[ |simplify2| \right]
  \end{alignat*}
}
%
Observe that each time we generate a value satisfying the first pattern matching
of the function |simplify|, we add two |Text| and one |Join| data constructors
to our random value.
%
The case of the second pattern matching of |simplify| follows analogously.
%
Note that the overall prediction cannot be applied if we also generate random
values containing function calls, as we cannot predict the output of an
arbitrary function.

>>>>

Vector $E[G_0]$ represents the initial distribution of constructors that our
generator produces, which simply consists of the generation probability of each
one.
%
The interesting aspect of the prediction mechanism is encoded in the matrix $M$,
known as a the \emph{mean matrix} of this stochastic process.
%
$M$ is a squared matrix with as rows and columns as different data constructors
involved in the generation process.
%
Each element $M_{i,j}$ of this matrix encodes the average number of data
constructors of kind $j$ that gets generated in a given generation, provided that we
generated a constructor of kind $i$ at the previous one.
%
In this sense, this matrix encodes the ``branching'' behavior of our random
generation from one generation to the next one.
%
Each element of the matrix can be automatically calculated by exploiting ADT
definitions, % \cite{DBLP:conf/haskell/MistaRH18}
%
% ---specially the recursive fields---
%
as well as the individual probability of generating each constructor.
%
For instance, the average number of |Text| data constructors that we will
generate provided that we generated a |Join| data constructor on the previous
level is calculated as follows:
%
$$ M_{\mathrm{Join, Text}} = 2\cdot p_{\mathrm{Text}} $$
%
where $2$ is the number of holes present when generating a partial ADT value
|Join| (i.e., |Join hole hole|) and $p_{\mathrm{Text}}$ is the probability of
individually generating the constructor |Text|.
%
This reasoning can be used to build the rest of the mean matrix analogously.

@@

each different pattern matching and function call as shown in Figure

@@

The new cells are filled as before: we need to consider the amount of holes when
generating partial pattern matching values and function calls as well as their
individual probabilities.
%
% Fortunately, it is possible to follow the same pattern as we did on our original
% work, this time considering the amount of recursive pattern variables if it the
% case of a pattern matching value being a father individual, and the amount of
% recursive arguments if we deal with a abstract interface function call as a
% father individual.
%
For instance, if we consider $P_j$ as the second pattern of function |simplify|
and $F_1$ as function |div|, then the marked cell above has the value
$2\cdot p_{div}$, i.e., the amount of holes in the partially generated pattern
|(Join (Join (Text s) hole) hole)|, where |s| is some random string, times the
probability to generate a call to function |div|.
%
The rest of this matrix can be computed analogously.

@@

As another contribution, we found that the whole prediction process can be
factored in terms of two vectors $\beta$ and $\mathcal{P}$, such that $\beta$
represents the number of holes in each partial ADT value that we generate,
whereas $\mathcal{P}$ simply represents the probability of generating that
partial ADT value.
% (this probability can be easily calculated based on the
% generation frequencies used in the random generator).
%
Then, the equation (\ref{eqn:prediction}) can be rewritten as:
%
\begin{align*}
  E[G_n]^T = \beta^T \cdot (\beta \cdot \mathcal{P}^T)^{n}
\end{align*}
%
% The vector $\beta$ can be obtained by analyzing the shape (namely holes) of each
% source of structural information that we consider, and joining them together.
%
For instance, $\beta$ and $\mathcal{P}$ for our generation specification of HTML
values are as shown in Figure \ref{fig:vectors}.
%
We note |simplify1| and |simplify2| to the patterns occurring in the first and
second clauses of |simplify|, respectively.
%(Dashed lines indicate the composition of the diffent sub-vectors
%that are calculated separately).

@@

It is possible to provide an overall prediction of the expected number of
constructors when restricting the generation process to only bare data
constructors and pattern matching values.
%
To achieve that, we should stop considering pattern matching values as atomic
constructions and start seeing them as compositions of several data
constructors.
%
In that manner, it is possible to obtain the expected \emph{total} number of
generated data constructors that our generators will produce---regardless if they
are generated on their own, or as part of a pattern matching value.
%
We note this number as $E^\downarrow\![\_]$ and, to calculate it, we only need
to add the expected number of bare constructors that are included within each
pattern matching.
%
For instance, we can calculate the total expected number of constructors |Text|
and |Join| that we will generate by simply expanding the expected number of
generated pattern matching values |simplify1| and |simplify2| into their
corresponding data constructors:
%
{\small
  \begin{alignat*}{4}
    &E^\downarrow\!\left[ |Text| \right]
    &= E\left[ |Text| \right]
      &+ 2 \cdot E\!\left[ |simplify1| \right]\
      &+\ 1 \cdot E\!\left[ |simplify2| \right] \\
    &E^\downarrow\!\left[ |Join| \right]
    &= E\left[ |Join| \right]
      &+ 1 \cdot E\!\left[ |simplify1| \right]\
      &+\ 2 \cdot E\!\left[ |simplify2| \right]
  \end{alignat*}
}
%
Observe that each time we generate a value satisfying the first pattern matching
of the function |simplify|, we add two |Text| and one |Join| data constructors
to our random value.
%
The case of the second pattern matching of |simplify| follows analogously.
%
Note that the overall prediction cannot be applied if we also generate random
values containing function calls, as we cannot predict the output of an
arbitrary function.
